### 2020-01-02 Draft/Draft.tex
after NY

\caption{{\small 1-member simulation for $\mathsf{m} = 10$, $\sigma_\mathsf{F} = 0.1$, and $\vass{T}{O}^{t = 0} = \vass{T}{A}^{t = 0} = 0.0$.}}

@@

\caption{{\small Fourier transforms $\hat{\mathsf{T}}_\mathsf{O}$ and $\hat{\mathsf{T}}_\mathsf{A}$ for $\mathsf{m} = 10$, $\sigma_\mathsf{F} = 0.1$.}}

@@

\caption{{\small Cross- and auto-correlation functions $\langle\mathsf{T_X,T_Y}\rangle$ for a 1-member simulation for $\mathsf{m} = 10$, $\sigma_\mathsf{F} = 0.1$, and $\vass{T}{O}^{t = 0} = \vass{T}{A}^{t = 0} = 0.0$. Note that the auto-correlation functions naturally peak at $\tau = 0$ while the cross-correlation peaks at $\tau < 0$ depicting the \tit{lagging effect} on the ocean.}}

@@

\caption{{\small Normalised probability densities (\tit{horizontal axes}) of peak lag times $|\taup|$ (\tit{vertical axes}) as a function of scale separation `$\mathsf{m}$'; $\sigma_\mathsf{F} = 0.1$, and $\vass{T}{O}^{t = 0} = \vass{T}{A}^{t = 0} = 1.0$. The solid lines denote normal distribution fits while the dashed lines denote skew-normal fits. Note the shift in the mode, the skewness and the spread of the distributions as a function of increasing values of $\mathsf{m}\in \{2,\,10,\,30,\,100\}$.}}

@@

{\noindent}where $\mathbf{T}_t^\mathsf{obs}$ and $\mathbf{T}_t^\mathsf{for}$ are the observation and forecast vectors. The analysed model error covariance matrix evolves as $\mathbf{P}_t^\mathsf{ana} = \mathbf{P}_t^\mathsf{for}\,[\mathbf{I} - \mathbf{K}_t]$ although this calculation is not required explicitly by the ensemble version of the Kalman filter. The analysed state $\mathbf{T}_t^\mathsf{ana}$ is finally translated in time from $t$ to $t + 1$ by the translation operation, $\mathbf{T}_{t+1}^\mathsf{for} = \mlin \cdot \mathbf{T}_{t}^\mathsf{ana}$, by numerically integrating the coupled stochastic differential equations\footnote{The expression \eqref{eq:linmodelvec} is of the \tit{Ito} form and its numerical integration is performed using \textsf{sdeint}.\textsf{itoint} algorithm available in Python's \textsf{SciPy} library. More specifically, \textsf{sdeint}.\textsf{itoint} uses the Euler-Maruyama algorithm to integrate the Ito equation.}  \eqref{eq:linmodel1}--\eqref{eq:linmodel2}. In our experiments, we reasonably assume the observation errors in the ocean and the atmosphere to be mutually uncorrelated and constant in time\footnote{We use the explicit form of $\mathbf{R}$ in our simulations instead of the ensemble form for simplicity.}, i.e.

@@

The observation vectors for the ocean and the atmosphere in our experiments are generated by perturbing a 1-member simulation of the model $\mlin$ with $\sigma_{\mathsf{O},\,\mathsf{obs}}$ and $\sigma_{\mathsf{A},\,\mathsf{obs}}$ respectively. Lastly, the Kalman Gain matrix $\mathbf{K}_t$ is explicitly written as 

@@

\boldsymbol{\sigma}_\mathsf{RMSE} = \sqrt{\sum_{\forall t}|\mathbf{T}_{t}^\mathsf{obs} - \mathbf{T}_{t}^\mathsf{ana}|^2}.

@@

\caption{{\small \textsf{RMSE} statistics derived from a 25--member {\enkf} simulation of the \textsf{SCDA} ($\boldsymbol{\sigma}_\mathsf{A/O}$), and the difference between the \textsf{WCDA} and the \textsf{SCDA} implementation ($\delta\boldsymbol{\sigma}_\mathsf{A/O}$); $\mathsf{m} = 10$. The model is spun up to stability during time $t \in [0, 50]$ whereas the {\rmse} means are calculated for time $t \in (275, 550]$. In this particular experiment, \textsf{SCDA} seems to perform marginally better than \textsf{WCDA} although this discrepancy is much smaller than the climatological background error due to the stochastic forcing term and should not be over-emphasised.}}

@@

{\noindent}We note that the spread of the ensemble in our simulation contracts over time since the model error covariance matrix evolves as $\mathbf{P}_t^\mathsf{ana} = \mathbf{P}_t^\mathsf{for}\,[\mathbf{I} - \mathbf{K}_t]$ besides the usual variation due to the model flow \citep{carrassi2018}. This leads to convergence issues and degradation in the performance of DA over time; we counter this effect by, \tit{a}) adaptively inflating the individual ensembles in the ocean and the atmosphere by a time-dependent factor $\alpha^{\mathsf{O/A}}_t$ such that the ensemble spread is preserved between the forecast and the analysis step, and \tit{b}) secondary multiplicative inflation of the ensemble for \textsf{SCDA} simulation by a constant factor $\gamma$, applied to both the oceanic as well as the atmospheric ensemble, on top of the adaptive inflation. 

@@

\caption{{\small The convergence of \textsf{SCDA} is probed by calculating the ratio between the {\rmse} and the spread of the ensemble for each sub-component over time $t$ for $\mathsf{m} = 10$. The criteria of convergence requires that this ratio tends to $\lesssim 1$ in the limit $t \rightarrow\infty$. We find that inflation is necessary to achieve convergence for both \textsf{SCDA} and \textsf{WCDA} (not shown).}}

@@

{\noindent}The mean values $\bar{\alpha}^{\mathsf{O/A}}_\mathsf{m}$ of the multiplicative inflationary factor $\alpha_t$ over time for a given `$\mathsf{m}$' is shown in figure \ref{fig:8} (bottom panel). It is noteworthy that the adaptive multiplicative inflation counters the contraction of ensemble due to the DA while the constant multiplicative inflation counters the deflation of ensemble due to the dissipative nature of the model. Thus, it follows that $\gamma$ must depend on the choice of `$\mathsf{m}$' in the model. In particular, $\gamma$ must decrease monotonically with increasing value of `$\mathsf{m}$'; we ran a tuning simulation to optimise the choice of $\gamma_\mathsf{m}$ and its results are shown in figure \ref{fig:8} (top panel).

@@

In this paper, we will attempt to quantify the effects of choices of $\tau_\mathsf{win}$ on $\delta\boldsymbol{\sigma}_\mathsf{RMSE}$. It must be noted that the optimal choice of $\tau_\mathsf{win}$ must depend on `$\mathsf{m}$' since $|\taup|$ depends on `$\mathsf{m}$'. Consequently, the results of the {\lacc} implementation compared with the \textsf{WCDA} and the \textsf{SCDA} are shown in figure \ref{fig:9} as a function of `$\mathsf{m}$' and $\tau_\mathsf{win}$. In principle, we expect that for larger scale separations, correspondingly longer leading averaged windows should maximise the cross-component {\snr}, thus leading to a larger disparity between the {\lacc} and the \textsf{SCDA/WCDA} implementations. However, we note that longer window lengths also decrease the frequency of the coupled cross-updates since this update is made only when preceding $\tau_\mathsf{win}$ observations in the atmosphere become available, which contribute toward diminishing returns of {\lacc} as seen in figure \ref{fig:9}. Overall, we find that the {\lacc} method performs better than the standard \textsf{WCDA} and \textsf{SCDA} implementations in the ocean when the noise is not too overwhelming. In particular, the impact of the frequency of stochastic forcing on the slower ocean sub-component is detrimental to the extent that {\lacc} and \textsf{SCDA} perform worse than \textsf{WCDA} in some cases whereas the atmosphere doesn't suffer from such an effect (i.e. \textsf{WCDA} is globally worse). 
\begin{figure}[H]
\includegraphics[width=78mm]{{Fig8a}.png}\vspace*{0.05in}
\includegraphics[width=78mm]{{Fig8b}.png}
\caption{{\small \tit{Top panel}: Calculated values of $\gamma_\mathsf{m}$ are shown on the vertical axes for different choices of of scale separation on the horizontal axes. We fit the data points with decaying exponential functional forms, where solid (--) and dashed (-$\,$-) lines represent the \textsf{SCDA} and the \textsf{WCDA} respectively, in order to derive a generalised analytical expression; using this formulae, we calculate the optimal choices of $\gamma_\mathsf{m}$ for any given `$\mathsf{m}$'. \tit{Bottom panel}: Mean values over time of the adaptive multiplicative inflation, i.e. $\bar{\alpha}^{\mathsf{O/A}}_\mathsf{m}$, are shown for different choices of scale separation for individual sub-components in the \textsf{SCDA} and the \textsf{WCDA} implementation.}}
\label{fig:8}
\end{figure}
\end{multicols}
\begin{figure}[H]
\centering\includegraphics[width=75mm]{{Fig9a}.png}\hspace*{0.05in}\rulesep\hspace*{0.05in}
\centering\includegraphics[width=75mm]{{Fig9c}.png}
\centering\includegraphics[width=75mm]{{Fig9b}.png}\hspace*{0.05in}\rulesep\hspace*{0.05in}
\centering\includegraphics[width=75mm]{{Fig9d}.png}
\caption{{\small \textsf{RMSE} statistics derived from a 25--member {\enkf} simulation as a function of  `$\mathsf{m}$' (\tit{vertical axes}) and $\tau_\mathsf{win}$ (\tit{horizontal axes}) showing the difference between the \textsf{WCDA} and the \textsf{LACC} implementation (including fully adaptive inflation with $\gamma_\mathsf{m}$ and $\alpha_{t,\mathsf{m}}$). The top panel shows the oceanic component while the bottom panel depicts the atmosphere. Note that the \textsf{SCDA} case depicted in figures \ref{fig:5}--\ref{fig:6} corresponds to $\tau_\mathsf{win} = 1$ in this plot. In order to compare the effect of frequency of stochastic forcing, we include the simulation results for when the forcing is applied every 10 time steps (\tit{right column}) instead of every iteration (\tit{left column}); note the higher efficiency of the \textsf{SCDA} implementation in the case of former less frequent stochastic forcing.}}
\label{fig:9}
\end{figure}
\newpage
\begin{multicols}{2}
{\noindent} 
\section{Extension of LACC to non-linear case}

>>>>

\caption{{\small 1-member simulation for $\mathsf{m} = 10$, $\sigma_\mathsf{F} = 1.0$, and $\vass{T}{O}^{t = 0} = \vass{T}{A}^{t = 0} = 0.0$.}}

@@

\caption{{\small Fourier transforms $\hat{\mathsf{T}}_\mathsf{O}$ and $\hat{\mathsf{T}}_\mathsf{A}$ for $\mathsf{m} = 10$, $\sigma_\mathsf{F} = 1.0$.}}

@@

\caption{{\small Cross- and auto-correlation functions $\langle\mathsf{T_X,T_Y}\rangle$ for a 1-member simulation for $\mathsf{m} = 10$, $\sigma_\mathsf{F} = 1.0$, and $\vass{T}{O}^{t = 0} = \vass{T}{A}^{t = 0} = 0.0$. Note that the auto-correlation functions naturally peak at $\tau = 0$ while the cross-correlation peaks at $\tau < 0$ depicting the \tit{lagging effect} on the ocean.}}

@@

\caption{{\small Normalised probability densities (\tit{horizontal axes}) of peak lag times $|\taup|$ (\tit{vertical axes}) as a function of scale separation `$\mathsf{m}$'; $\sigma_\mathsf{F} = 1.0$, and $\vass{T}{O}^{t = 0} = \vass{T}{A}^{t = 0} = 0.0$. The solid lines denote normal distribution fits while the dashed lines denote skew-normal fits. Note the shift in the mode, the skewness and the spread of the distributions as a function of increasing values of $\mathsf{m}\in \{2,\,10,\,30,\,100\}$.}}

@@

{\noindent}where $\mathbf{T}_t^\mathsf{obs}$ and $\mathbf{T}_t^\mathsf{for}$ are the observation and forecast vectors. The analysed model error covariance matrix evolves as $\mathbf{P}_t^\mathsf{ana} = \mathbf{P}_t^\mathsf{for}\,[\mathbf{I} - \mathbf{K}_t]$ although this calculation is not required explicitly by the ensemble version of the Kalman filter. The analysed state $\mathbf{T}_t^\mathsf{ana}$ is finally translated in time from $t$ to $t + 1$ by the translation operation, $\mathbf{T}_{t+1}^\mathsf{for} = \mlin \cdot \mathbf{T}_{t}^\mathsf{ana}$, by numerically integrating the coupled stochastic differential equations\footnote{The expression \eqref{eq:linmodelvec} is of the \tit{Ito} form and its numerical integration is performed using \textsf{sdeint}.\textsf{itoint} algorithm available in Python's \textsf{SciPy} library. More specifically, \textsf{sdeint}.\textsf{itoint} uses the Euler-Maruyama algorithm to integrate the Ito equation.}  \eqref{eq:linmodel1}--\eqref{eq:linmodel2}. In our experiments, we reasonably assume the observation errors in the ocean and the atmosphere to be mutually uncorrelated and constant in time\footnote{We use the explicit form of $\mathbf{R}$ in our simulations instead of the ensemble form for simplicity. Note that each ensemble member receives its unique perturbed version of the truth defined by $\mathbf{R}$.}, i.e.

@@

The \tit{true} observation vectors, namely $\mathbf{T}_{t}^\mathsf{true}$, for the ocean and the atmosphere in our experiments are generated by perturbing a 1-member simulation of the model $\mlin$ with $\sigma_{\mathsf{O},\,\mathsf{obs}}$ and $\sigma_{\mathsf{A},\,\mathsf{obs}}$ respectively. Lastly, the Kalman Gain matrix $\mathbf{K}_t$ is explicitly written as 

@@

\boldsymbol{\sigma}_\mathsf{RMSE} = \sqrt{\sum_{\forall t}|\mathbf{T}_{t}^\mathsf{true} - \mathbf{T}_{t}^\mathsf{ana}|^2}.

@@

\caption{{\small \textsf{RMSE} statistics derived from a 25--member {\enkf} simulation of the \textsf{SCDA} ($\boldsymbol{\sigma}_\mathsf{A/O}$), and the difference between the \textsf{WCDA} and the \textsf{SCDA} implementation ($\delta\boldsymbol{\sigma}_\mathsf{A/O}$); $\mathsf{m} = 10$. The model is spun up to stability during time $t \in [0, 50]$ whereas the {\rmse} means are calculated for time $t \in (275, 550]$. In this particular experiment, \textsf{SCDA} seems to perform marginally better in the slower ocean component than \textsf{WCDA} although this discrepancy is much smaller than the climatological background error due to the stochastic forcing term and should not be over-emphasised.}}

@@

{\noindent}We note that the spread of the ensemble in our simulation contracts over time since the model error covariance matrix evolves as $\mathbf{P}_t^\mathsf{ana} = \mathbf{P}_t^\mathsf{for}\,[\mathbf{I} - \mathbf{K}_t]$ besides the usual variation due to the model flow \citep{carrassi2018}. This leads to convergence issues and degradation in the performance of DA over time; we counter this effect by incorporating a constant multiplicative inflationary factor of the ensemble for the \textsf{SCDA} simulation, denoted by $\gamma$, applied to both the oceanic as well as the atmospheric ensemble. 

@@

\caption{{\small The convergence of \textsf{SCDA} is probed by calculating the ratio between the {\rmse} and the spread of the ensemble for each sub-component over time $t$ for $\mathsf{m} = 10$. The criteria of convergence requires that this ratio tends to $\lesssim 1$ in the limit $t \rightarrow\infty$. We find that inflation is necessary to achieve convergence for both the \textsf{SCDA} and the \textsf{WCDA} (not shown).}}

@@

\includegraphics[width=78mm]{{Fig8}.png}
\caption{{\small Calculated values of $\gamma_\mathsf{m}$ are shown on the vertical axes for different choices of of scale separation on the horizontal axes. We fit the data points with decaying exponential functional forms, marked by dashed (--$\,$--) lines, in order to derive a generalised analytical expression; using this formulae, we calculate the optimal choices of $\gamma_\mathsf{m}$ for any given `$\mathsf{m}$'. Note that both the \textsf{WCDA} and the \textsf{SCDA} implementations are inflated by the same value of $\gamma_\mathsf{m}$.}}
\label{fig:8}
{\noindent}The values of the constant multiplicative inflationary factor $\gamma$ is shown in figure \ref{fig:8}. It is noteworthy that the constant multiplicative inflation counters the deflation of ensemble due to the dissipative nature of the model. Thus, it follows that $\gamma$ must depend on the choice of `$\mathsf{m}$' in the model. In particular, $\gamma$ must decrease monotonically with increasing value of `$\mathsf{m}$'; we ran a tuning simulation to optimise the choice of $\gamma_\mathsf{m}$ and its results are shown in figure \ref{fig:8}.

@@

\centering\includegraphics[width=78mm]{{Fig9a}.png}
\centering\includegraphics[width=78mm]{{Fig9b}.png}
\caption{{\small \textsf{RMSE} statistics derived from a 25--member {\enkf} simulation as a function of  `$\mathsf{m}$' (\tit{vertical axes}) and $\tau_\mathsf{win}$ (\tit{horizontal axes}) showing the difference between the \textsf{WCDA} and the \textsf{SCDA}/\textsf{LACC} implementations captured by $\delta\boldsymbol{\sigma}_\mathsf{A/O}$; the top panel shows the oceanic component while the bottom panel depicts the atmosphere. Note that the \textsf{SCDA} case depicted in figures \ref{fig:5}--\ref{fig:6} corresponds to $\tau_\mathsf{win} = 1$ in this plot. In other words, \textsf{LACC}$_{[\tau_\mathsf{win} = 1]}$ $\equiv$ \textsf{SCDA}.}}
\label{fig:9}
{\noindent}In this paper, we will attempt to quantify the effects of choices of $\tau_\mathsf{win}$ on $\delta\boldsymbol{\sigma}_\mathsf{RMSE}$. It must be noted that the optimal choice of $\tau_\mathsf{win}$ must depend on `$\mathsf{m}$' since $|\taup|$ depends on `$\mathsf{m}$'. Consequently, the results of the {\lacc} implementation compared with the \textsf{WCDA} and the \textsf{SCDA} are shown in figure \ref{fig:9} as a function of `$\mathsf{m}$' and $\tau_\mathsf{win}$. In principle, we expect that for larger scale separations, correspondingly longer leading averaged windows should maximise the cross-component {\snr}, thus leading to a larger disparity between the {\lacc} and the \textsf{WCDA} implementations. However, we note that longer window lengths also decrease the frequency of the coupled cross-updates since this update is made only when preceding $\tau_\mathsf{win}$ observations in the atmosphere become available, which contribute toward diminishing returns of {\lacc} as seen in figure \ref{fig:9}. Overall, we find that the {\lacc} and the \textsf{SCDA} methods perform better than the standard \textsf{WCDA} implementation in the ocean whereas the atmosphere almost always suffers when the coupled cross-updates are included. 
\newpage
{\noindent} 
\section{Extension of LACC to non-linear case}
